---
title: "Contest-Interaction ABM Summary Tables for Publication -- Deterministic"
author: "C.J. O'Connor-Coates"
date: "2023-01-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#-------------------------------------------------------------------------------------------------------------------------

# All data was generated in NetLogo Agent-Based Models (ABM) and imported into this program for analysis. These data and analyses are used in the publication "Steep hierarchies without skew? Modeling how ecology and decision-making shape despotism of relationships" by Marcy S. Ekanayake-Weber, Christopher J. O'Connor-Coates, and Andreas Koenig.

# The NetLogo model was created by Marcy S. Ekanayake-Weber and Christopher J. O'Connor-Coates. The following R-code was written by Christopher J. O'Connor-Coates. The code for the Triangle Transitivity Function was written by Shizuka & McDonald (2012). For questions regarding the R-code email Christopher J. O'Connor-Coates at christopher.oconnor-coates@stonybrook.edu.

#-------------------------------------------------------------------------------------------------------------------------

#-------------------------------------------------------------------------------------------------------------------------

# DEFINITIONS:
# 1. Knowledge (k): Individuals know of either their own or their opponent's Resource Holding Potential (RHP)
# 2. History (h): Individuals know of either their own or their opponent's fighting history, including how often theiy won or lost conflicts
# 3. Mutual (m): Individuals have knowledge of both their own and their opponent's RHP or History
# 4. Self (s): Individuals have knowledge of only their own RHP or History
# 5. Opponent (o): Individuals have knowledge of only their opponent's RHP or History
# 6. Deterministic (d): Scenarios in which fight outcomes were determined by the strength of an individual's RHP. Individuals with higher RHP values always won escalated conflicts.
# 7. Probabilistic (p): Scenarios in which fight outcomes were determined by a probability calculated in the NetLogo program. Individuals with higher RHP values are more likely to win escalated conflicts, but there is also a (smaller) chance that the individual with lower RHP could win the conflict.
# 8. Initiator Wins (iw; i): Scenarios in which the escalated conflict is always won by the individual which initiated the conflict.
# 9. Sigmoid Function (sf): Scenarios in which fights were escalated through a cost-benefit analysis that was modeled as a sigmoid function.
# 10. Clumped Distribution (cd; c): Resources were arranged in the landscape such that they only appeared in clumps; can also be called a heterogenous distribution
# 11. Uniform Distribution (ud; u): Resources were arranged in the landscape such that they were evenly distributed across the area; can also be called a homogenous distribution
# 12. Avoid: An individual avoided an escalation/conflict
# 13. Victory: An individual won an escalation/conflict
# 14. Foraging Efficiency: An Individual's Energy Intake Over Time

#ABBREVIATIONS:
# 1. inter.mat: Interaction Matrices
# 2. ep: Proportion of Escalation
# 3. t.tri: Triangle Transitivity
# 4. dci: Directional Conistency Index
# 5. Steep: steepness

#-------------------------------------------------------------------------------------------------------------------------


#-------------------------------------------------------------------------------------------------------------------------

# TO USE CODE SET YOUR WORKING DIRECTORY FILEPATHS (WHERE INDICATED) TO WHERE YOU HAVE SAVED THE DATA FILES.
# INDICATED FILEPATHS LOOK LIKE: setwd("~/SET/YOUR/WORKING/DIRECTORY/...")

#-------------------------------------------------------------------------------------------------------------------------



## Summary Tables For Publication
```{r}
#Subset attack proportions data into individual data frames based on the distribution type and assessment information.

dist.split.d <- split(attack.prop.2, attack.prop.2$X.1) #Splits attack proportions into separate data frames for "clumped" and "uniform" distributions (line 17)
new.dist <- c("clumped.attack.prop.d", "uniform.attack.prop.d")
for (i in 1:length(dist.split.d)) { #Variable "i" represents data by distribution
  assign(new.dist[i], dist.split.d[[i]]) #Assigns data to the named dataframes above (line 17)
}


clump.attack.prop.split.d <- split(clumped.attack.prop.d, clumped.attack.prop.d$combo2) #Splits attack proportions into separate data frames that occurred the "clumped" distribution based on assessment information (lines 21:26)
new.names.c.d <- c("hm.attack.prop.c.d",
                   "km.attack.prop.c.d",
                   "ho.attack.prop.c.d",
                   "ko.attack.prop.c.d",
                   "hs.attack.prop.c.d",
                   "ks.attack.prop.c.d")
uni.attack.prop.split.d <- split(uniform.attack.prop.d, uniform.attack.prop.d$combo2) #Splits attack proportions into separate data frames that occurred the "uniform" distribution based on assessment information (lines 28:33)
new.names.u.d <- c("hm.attack.prop.u.d", 
                   "km.attack.prop.u.d", 
                   "ho.attack.prop.u.d", 
                   "ko.attack.prop.u.d", 
                   "hs.attack.prop.u.d", 
                   "ks.attack.prop.u.d")
for (j in 1:length(clump.attack.prop.split.d)) { #Variable "j" represents data in the clumped distribution by assessment information
  for (k in 1:length(uni.attack.prop.split.d)) { #Variable "k" represents data in the uniform distribution by assessment information
        assign(new.names.c.d[j], clump.attack.prop.split.d[[j]]) #Assigns data to the named dataframes above (lines 21:26)
        assign(new.names.u.d[k], uni.attack.prop.split.d[[k]]) #Assigns data to the named dataframes above (lines 28:33)
  }
}
```

```{r Deterministic Clumped Summary Table}
# Generate summary tables of the deterministic clumped data for publication:

# Knowledge mutual
km.st<-overall.ss.deter[overall.ss.deter$combo=="mutual rhp clumped",]
  km.tt<-mean(km.st$triangle.transitivity)
  km.dci<-mean(km.st$dci)
  
  km.poa<-mean(km.attack.prop.c.d$X.10)
  
  km.steep<-abs(mean(km.st$steepness))
  km.ov<-data.frame(Knowledge.Mutual = c(km.poa,km.dci,km.tt,km.steep,avg.int.km.dc,avg.av.km.dc))

# Knowledge self
ks.st<-overall.ss.deter[overall.ss.deter$combo=="self rhp clumped",]
  ks.tt<-mean(ks.st$triangle.transitivity)
  ks.dci<-mean(ks.st$dci)
  ks.poa<-mean(ks.attack.prop.c.d$X.10)
  ks.steep<-abs(mean(ks.st$steepness))
  ks.ov<-data.frame(Knowledge.Self = c(ks.poa,ks.dci,ks.tt,ks.steep,avg.int.ks.dc,avg.av.ks.dc))

# Knowledge opponent
ko.st<-overall.ss.deter[overall.ss.deter$combo=="opponent rhp clumped",]
  ko.tt<-mean(ko.st$triangle.transitivity)
  ko.dci<-mean(ko.st$dci)
  ko.poa<-mean(ko.attack.prop.c.d$X.10)
  ko.steep<-abs(mean(ko.st$steepness))
  ko.ov<-data.frame(Knowledge.Opponent = c(ko.poa,ko.dci,ko.tt,ko.steep,avg.int.ko.dc,avg.av.ko.dc))

# history mutual
hm.st<-overall.ss.deter[overall.ss.deter$combo=="mutual history clumped",]
  hm.tt<-mean(hm.st$triangle.transitivity)
  hm.dci<-mean(hm.st$dci)
  hm.poa<-mean(hm.attack.prop.c.d$X.10)
  hm.steep<-abs(mean(hm.st$steepness))
  hm.ov<-data.frame(History.Mutual = c(hm.poa,hm.dci,hm.tt,hm.steep,avg.int.hm.dc,avg.av.hm.dc))

# history self
hs.st<-overall.ss.deter[overall.ss.deter$combo=="self history clumped",]
  hs.tt<-mean(hs.st$triangle.transitivity)
  hs.dci<-mean(hs.st$dci)
  hs.poa<-mean(hs.attack.prop.c.d$X.10)
  hs.steep<-abs(mean(hs.st$steepness))
  hs.ov<-data.frame(History.Self = c(hs.poa,hs.dci,hs.tt,hs.steep,avg.int.hs.dc,avg.av.hs.dc))

# history opponent
ho.st<-overall.ss.deter[overall.ss.deter$combo=="opponent history clumped",]
  ho.tt<-mean(ho.st$triangle.transitivity)
  ho.dci<-mean(ho.st$dci)
  ho.poa<-mean(ho.attack.prop.c.d$X.10)
  ho.steep<-abs(mean(ho.st$steepness))
  ho.ov<-data.frame(History.Opponent = c(ho.poa,ho.dci,ho.tt,ho.steep,avg.int.ho.dc,avg.av.ho.dc))

# Generate overall data frame of the summary tables above:
overall.c.st<-data.frame(kno.mut=km.ov,hist.mut=hm.ov,kno.self=ks.ov,hist.self=hs.ov,kno.opp=ko.ov,hist.opp=ho.ov)
row.names(overall.c.st)<-c("Proportion of Attack","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.c.st,"~/SET/YOUR/FILEPATH/overall_summary_table_dc.csv")
```

```{r Deterministic Uniform Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

# Knowledge mutual
km.st.u<-overall.ss.deter[overall.ss.deter$combo=="mutual rhp Uniform",]
  km.tt.u<-mean(km.st.u$triangle.transitivity)
  km.dci.u<-mean(km.st.u$dci)
  km.poa.u<-mean(km.attack.prop.u.d$X.10)
  km.steep.u<-abs(mean(km.st.u$steepness))
  km.ov.u<-data.frame(Knowledge.Mutual = c(km.poa.u,km.dci.u,km.tt.u,km.steep.u,avg.int.km.du,avg.av.km.du))

# Knowledge self  
ks.st.u<-overall.ss.deter[overall.ss.deter$combo=="self rhp Uniform",]
  ks.tt.u<-mean(ks.st.u$triangle.transitivity)
  ks.dci.u<-mean(ks.st.u$dci)
  ks.poa.u<-mean(ks.attack.prop.u.d$X.10)
  ks.steep.u<-abs(mean(ks.st.u$steepness))
  ks.ov.u<-data.frame(Knowledge.Self = c(ks.poa.u,ks.dci.u,ks.tt.u,ks.steep.u,avg.int.ks.du,avg.av.ks.du))

# Knowledge opponent
ko.st.u<-overall.ss.deter[overall.ss.deter$combo=="opponent rhp Uniform",]
  ko.tt.u<-mean(ko.st.u$triangle.transitivity)
  ko.dci.u<-mean(ko.st.u$dci)
  ko.poa.u<-mean(ko.attack.prop.u.d$X.10)
  ko.steep.u<-abs(mean(ko.st.u$steepness))
  ko.ov.u<-data.frame(Knowledge.Opponent = c(ko.poa.u,ko.dci.u,ko.tt.u,ko.steep.u,avg.int.ko.du,avg.av.ko.du))

# History mutual
hm.st.u<-overall.ss.deter[overall.ss.deter$combo=="mutual history Uniform",]
  hm.tt.u<-mean(hm.st.u$triangle.transitivity)
  hm.dci.u<-mean(hm.st.u$dci)
  hm.poa.u<-mean(hm.attack.prop.u.d$X.10)
  hm.steep.u<-abs(mean(hm.st.u$steepness))
  hm.ov.u<-data.frame(History.Mutual = c(hm.poa.u,hm.dci.u,hm.tt.u,hm.steep.u,avg.int.hm.du,avg.av.hm.du))

# History self
hs.st.u<-overall.ss.deter[overall.ss.deter$combo=="self history Uniform",]
  hs.tt.u<-mean(hs.st.u$triangle.transitivity)
  hs.dci.u<-mean(hs.st.u$dci)
  hs.poa.u<-mean(hs.attack.prop.u.d$X.10)
  hs.steep.u<-abs(mean(hs.st.u$steepness))
  hs.ov.u<-data.frame(History.Self = c(hs.poa.u,hs.dci.u,hs.tt.u,hs.steep.u,avg.int.hs.du,avg.av.hs.du))

# History opponent
ho.st.u<-overall.ss.deter[overall.ss.deter$combo=="opponent history Uniform",]
  ho.tt.u<-mean(ho.st.u$triangle.transitivity)
  ho.dci.u<-mean(ho.st.u$dci)
  ho.poa.u<-mean(ho.attack.prop.u.d$X.10)
  ho.steep.u<-abs(mean(ho.st.u$steepness))
  ho.ov.u<-data.frame(History.Opponent = c(ho.poa.u,ho.dci.u,ho.tt.u,ho.steep.u,avg.int.ho.du,avg.av.ho.du))

# Generate overall data frame of the summary tables above:
overall.c.st.u<-data.frame(kno.mut=km.ov.u,hist.mut=hm.ov.u,kno.self=ks.ov.u,hist.self=hs.ov.u,kno.opp=ko.ov.u,hist.opp=ho.ov.u)
row.names(overall.c.st.u)<-c("Proportion of Attack","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.c.st.u,"~/SET/YOUR/FILEPATH/overall_summary_table_du.csv")
```

```{r Deterministic Clumped Avoid Summary Table}
# Generate summary tables of the deterministic clumped avoid data for publication:

# Knowledge mutual
km.st.avoid<-overall.ss.deter.clumped.avoid[overall.ss.deter.clumped.avoid$combo=="mutual rhp clumped",]
  km.tt.avoid<-mean(km.st.avoid$triangle.transitivity)
  km.dci.avoid<-mean(km.st.avoid$dci)
  km.poa.avoid<-mean(km.attack.prop.c.d$rate.avoids)
  km..steep.avoid<-abs(mean(km.st.avoid$steepness))
  km.ov.avoid<-data.frame(Knowledge.Mutual = c(km.poa.avoid,km.dci.avoid,km.tt.avoid,km..steep.avoid,avg.int.km.acd,avg.av.km.acd))

# Knowledge self  
ks.st.avoid<-overall.ss.deter.clumped.avoid[overall.ss.deter.clumped.avoid$combo=="self rhp clumped",]
  ks.tt.avoid<-mean(ks.st.avoid$triangle.transitivity)
  ks.dci.avoid<-mean(ks.st.avoid$dci)
  ks.poa.avoid<-mean(ks.attack.prop.c.d$rate.avoids)
  ks..steep.avoid<-abs(mean(ks.st.avoid$steepness))
  ks.ov.avoid<-data.frame(Knowledge.Self = c(ks.poa.avoid,ks.dci.avoid,ks.tt.avoid,ks..steep.avoid,avg.int.ks.acd,avg.av.ks.acd))

# Knowledge opponent
ko.st.avoid<-overall.ss.deter.clumped.avoid[overall.ss.deter.clumped.avoid$combo=="opponent rhp clumped",]
  ko.tt.avoid<-mean(ko.st.avoid$triangle.transitivity)
  ko.dci.avoid<-mean(ko.st.avoid$dci)
  ko.poa.avoid<-mean(ko.attack.prop.c.d$rate.avoids)
  ko..steep.avoid<-abs(mean(ko.st.avoid$steepness))
  ko.ov.avoid<-data.frame(Knowledge.Opponent = c(ko.poa.avoid,ko.dci.avoid,ko.tt.avoid,ko..steep.avoid,avg.int.ko.acd,avg.av.ko.acd))

# History mutual
hm.st.avoid<-overall.ss.deter.clumped.avoid[overall.ss.deter.clumped.avoid$combo=="mutual history clumped",]
  hm.tt.avoid<-mean(hm.st.avoid$triangle.transitivity)
  hm.dci.avoid<-mean(hm.st.avoid$dci)
  hm.poa.avoid<-mean(hm.attack.prop.c.d$rate.avoids)
  hm..steep.avoid<-abs(mean(hm.st.avoid$steepness))
  hm.ov.avoid<-data.frame(History.Mutual = c(hm.poa.avoid,hm.dci.avoid,hm.tt.avoid,hm..steep.avoid,avg.int.hm.acd,avg.av.km.acd))

# History self
hs.st.avoid<-overall.ss.deter.clumped.avoid[overall.ss.deter.clumped.avoid$combo=="self history clumped",]
  hs.tt.avoid<-mean(hs.st.avoid$triangle.transitivity)
  hs.dci.avoid<-mean(hs.st.avoid$dci)
  hs.poa.avoid<-mean(hs.attack.prop.c.d$rate.avoids)
  hs..steep.avoid<-abs(mean(hs.st.avoid$steepness))
  hs.ov.avoid<-data.frame(History.Self = c(hs.poa.avoid,hs.dci.avoid,hs.tt.avoid,hs..steep.avoid,avg.int.hs.acd,avg.av.hs.acd))

# History opponent
ho.st.avoid<-overall.ss.deter.clumped.avoid[overall.ss.deter.clumped.avoid$combo=="opponent history clumped",]
  ho.tt.avoid<-mean(ho.st.avoid$triangle.transitivity)
  ho.dci.avoid<-mean(ho.st.avoid$dci)
  ho.poa.avoid<-mean(ho.attack.prop.c.d$rate.avoids)
  ho..steep.avoid<-abs(mean(ho.st.avoid$steepness))
  ho.ov.avoid<-data.frame(History.Opponent = c(ho.poa.avoid,ho.dci.avoid,ho.tt.avoid,ho..steep.avoid,avg.int.ho.acd,avg.av.ho.acd))

# Generate overall data frame of the summary tables above:
overall.c.st.avoid<-data.frame(kno.mut=km.ov.avoid,hist.mut=hm.ov.avoid,kno.self=ks.ov.avoid,hist.self=hs.ov.avoid,kno.opp=ko.ov.avoid,hist.opp=ho.ov.avoid)
row.names(overall.c.st.avoid)<-c("Rate of Avoids","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.c.st.avoid,"~/SET/YOUR/FILEPATH/overall_clump_avoid_summary_table_dc.csv")
```

```{r Deterministic Clumped Attacks Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

# Knowledge mutual
km.st.attacks<-overall.ss.deter.clumped.attacks[overall.ss.deter.clumped.attacks$combo=="mutual rhp clumped",]
  km.tt.attacks<-mean(km.st.attacks$triangle.transitivity)
  km.dci.attacks<-mean(km.st.attacks$dci)
  km.poa.attacks<-mean(km.attack.prop.c.d$rate.attacks)
  km..steep.attacks<-abs(mean(km.st.attacks$steepness))
  km.ov.attacks<-data.frame(Knowledge.Mutual = c(km.poa.attacks,km.dci.attacks,km.tt.attacks,km..steep.attacks,avg.int.km.acd,avg.av.km.acd))

# Knowledge self  
ks.st.attacks<-overall.ss.deter.clumped.attacks[overall.ss.deter.clumped.attacks$combo=="self rhp clumped",]
  ks.tt.attacks<-mean(ks.st.attacks$triangle.transitivity)
  ks.dci.attacks<-mean(ks.st.attacks$dci)
  ks.poa.attacks<-mean(ks.attack.prop.c.d$rate.attacks)
  ks..steep.attacks<-abs(mean(ks.st.attacks$steepness))
  ks.ov.attacks<-data.frame(Knowledge.Self = c(ks.poa.attacks,ks.dci.attacks,ks.tt.attacks,ks..steep.attacks,avg.int.ks.acd,avg.av.ks.acd))

# Knowledge opponent
ko.st.attacks<-overall.ss.deter.clumped.attacks[overall.ss.deter.clumped.attacks$combo=="opponent rhp clumped",]
  ko.tt.attacks<-mean(ko.st.attacks$triangle.transitivity)
  ko.dci.attacks<-mean(ko.st.attacks$dci)
  ko.poa.attacks<-mean(ko.attack.prop.c.d$rate.attacks)
  ko..steep.attacks<-abs(mean(ko.st.attacks$steepness))
  ko.ov.attacks<-data.frame(Knowledge.Opponent = c(ko.poa.attacks,ko.dci.attacks,ko.tt.attacks,ko..steep.attacks,avg.int.ko.acd,avg.av.ko.acd))

# History mutual
hm.st.attacks<-overall.ss.deter.clumped.attacks[overall.ss.deter.clumped.attacks$combo=="mutual history clumped",]
  hm.tt.attacks<-mean(hm.st.attacks$triangle.transitivity)
  hm.dci.attacks<-mean(hm.st.attacks$dci)
  hm.poa.attacks<-mean(hm.attack.prop.c.d$rate.attacks)
  hm..steep.attacks<-abs(mean(hm.st.attacks$steepness))
  hm.ov.attacks<-data.frame(History.Mutual = c(hm.poa.attacks,hm.dci.attacks,hm.tt.attacks,hm..steep.attacks,avg.int.hm.acd,avg.av.hm.acd))

# History self
hs.st.attacks<-overall.ss.deter.clumped.attacks[overall.ss.deter.clumped.attacks$combo=="self history clumped",]
  hs.tt.attacks<-mean(hs.st.attacks$triangle.transitivity)
  hs.dci.attacks<-mean(hs.st.attacks$dci)
  hs.poa.attacks<-mean(hs.attack.prop.c.d$rate.attacks)
  hs..steep.attacks<-abs(mean(hs.st.attacks$steepness))
  hs.ov.attacks<-data.frame(History.Self = c(hs.poa.attacks,hs.dci.attacks,hs.tt.attacks,hs..steep.attacks,avg.int.hs.acd,avg.av.hs.acd))

# History opponent
ho.st.attacks<-overall.ss.deter.clumped.attacks[overall.ss.deter.clumped.attacks$combo=="opponent history clumped",]
  ho.tt.attacks<-mean(ho.st.attacks$triangle.transitivity)
  ho.dci.attacks<-mean(ho.st.attacks$dci)
  ho.poa.attacks<-mean(ho.attack.prop.c.d$rate.attacks)
  ho..steep.attacks<-abs(mean(ho.st.attacks$steepness))
  ho.ov.attacks<-data.frame(History.Opponent = c(ho.poa.attacks,ho.dci.attacks,ho.tt.attacks,ho..steep.attacks,avg.int.ho.acd,avg.av.ho.acd))

# Generate overall data frame of the summary tables above:
overall.c.st.attacks<-data.frame(kno.mut=km.ov.attacks,hist.mut=hm.ov.attacks,kno.self=ks.ov.attacks,hist.self=hs.ov.attacks,kno.opp=ko.ov.attacks,hist.opp=ho.ov.attacks)
row.names(overall.c.st.attacks)<-c("Rate of Attacks","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks","Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.c.st.attacks,"~/SET/YOUR/FILEPATH/overall_clump_attacks_summary_table_dc.csv")
```

```{r Deterministic Uniform Avoid Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

#Knowledge mutual
km.st.avoid<-overall.ss.deter.uniform.avoid[overall.ss.deter.uniform.avoid$combo=="mutual rhp Uniform",]
  km.tt.avoid<-mean(km.st.avoid$triangle.transitivity)
  km.dci.avoid<-mean(km.st.avoid$dci)
  km.poa.avoid<-mean(km.attack.prop.u.d$rate.avoids)
  km..steep.avoid<-abs(mean(km.st.avoid$steepness))
  km.ov.avoid<-data.frame(Knowledge.Mutual = c(km.poa.avoid,km.dci.avoid,km.tt.avoid,km..steep.avoid,avg.int.km.adu,avg.av.km.adu))

# Knowledge self 
ks.st.avoid<-overall.ss.deter.uniform.avoid[overall.ss.deter.uniform.avoid$combo=="self rhp Uniform",]
  ks.tt.avoid<-mean(ks.st.avoid$triangle.transitivity)
  ks.dci.avoid<-mean(ks.st.avoid$dci)
  ks.poa.avoid<-mean(ks.attack.prop.u.d$rate.avoids)
  ks..steep.avoid<-abs(mean(ks.st.avoid$steepness))
  ks.ov.avoid<-data.frame(Knowledge.Self = c(ks.poa.avoid,ks.dci.avoid,ks.tt.avoid,ks..steep.avoid,avg.int.ks.adu,avg.av.ks.adu))

# Knowledge opponent
ko.st.avoid<-overall.ss.deter.uniform.avoid[overall.ss.deter.uniform.avoid$combo=="opponent rhp Uniform",]
  ko.tt.avoid<-mean(ko.st.avoid$triangle.transitivity)
  ko.dci.avoid<-mean(ko.st.avoid$dci)
  ko.poa.avoid<-mean(ko.attack.prop.u.d$rate.avoids)
  ko..steep.avoid<-abs(mean(ko.st.avoid$steepness))
  ko.ov.avoid<-data.frame(Knowledge.Opponent = c(ko.poa.avoid,ko.dci.avoid,ko.tt.avoid,ko..steep.avoid,avg.int.ko.adu,avg.av.ko.adu))

# History mutual
hm.st.avoid<-overall.ss.deter.uniform.avoid[overall.ss.deter.uniform.avoid$combo=="mutual history Uniform",]
  hm.tt.avoid<-mean(hm.st.avoid$triangle.transitivity)
  hm.dci.avoid<-mean(hm.st.avoid$dci)
  hm.poa.avoid<-mean(hm.attack.prop.u.d$rate.avoids)
  hm..steep.avoid<-abs(mean(hm.st.avoid$steepness))
  hm.ov.avoid<-data.frame(History.Mutual = c(hm.poa.avoid,hm.dci.avoid,hm.tt.avoid,hm..steep.avoid,avg.int.hm.adu,avg.av.hm.adu))

# History self
hs.st.avoid<-overall.ss.deter.uniform.avoid[overall.ss.deter.uniform.avoid$combo=="self history Uniform",]
  hs.tt.avoid<-mean(hs.st.avoid$triangle.transitivity)
  hs.dci.avoid<-mean(hs.st.avoid$dci)
  hs.poa.avoid<-mean(hs.attack.prop.u.d$rate.avoids)
  hs..steep.avoid<-abs(mean(hs.st.avoid$steepness))
  hs.ov.avoid<-data.frame(History.Self = c(hs.poa.avoid,hs.dci.avoid,hs.tt.avoid,hs..steep.avoid,avg.int.hs.adu,avg.av.hs.adu))

# History opponent
ho.st.avoid<-overall.ss.deter.uniform.avoid[overall.ss.deter.uniform.avoid$combo=="opponent history Uniform",]
  ho.tt.avoid<-mean(ho.st.avoid$triangle.transitivity)
  ho.dci.avoid<-mean(ho.st.avoid$dci)
  ho.poa.avoid<-mean(ho.attack.prop.u.d$rate.avoids)
  ho..steep.avoid<-abs(mean(ho.st.avoid$steepness))
  ho.ov.avoid<-data.frame(History.Opponent = c(ho.poa.avoid,ho.dci.avoid,ho.tt.avoid,ho..steep.avoid,avg.int.ho.adu,avg.av.ho.adu))

# Generate overall data frame of the summary tables above:
overall.u.st.avoid<-data.frame(kno.mut=km.ov.avoid,hist.mut=hm.ov.avoid,kno.self=ks.ov.avoid,hist.self=hs.ov.avoid,kno.opp=ko.ov.avoid,hist.opp=ho.ov.avoid)
row.names(overall.u.st.avoid)<-c("Rate of Avoids","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.u.st.avoid,"~/SET/YOUR/FILEPATH/overall_uniform_avoid_summary_table_dc.csv")
```

```{r Deterministic Uniform Attacks Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

#knowledge mutual
km.st.attacks<-overall.ss.deter.uniform.attacks[overall.ss.deter.uniform.attacks$combo=="mutual rhp Uniform",]
  km.tt.attacks<-mean(km.st.attacks$triangle.transitivity)
  km.dci.attacks<-mean(km.st.attacks$dci)
  km.poa.attacks<-mean(km.attack.prop.u.d$rate.attacks)
  km..steep.attacks<-abs(mean(km.st.attacks$steepness))
  km.ov.attacks<-data.frame(Knowledge.Mutual = c(km.poa.attacks,km.dci.attacks,km.tt.attacks,km..steep.attacks,avg.int.km.atdu,avg.av.km.atdu))

# Knowledge self  
ks.st.attacks<-overall.ss.deter.uniform.attacks[overall.ss.deter.uniform.attacks$combo=="self rhp Uniform",]
  ks.tt.attacks<-mean(ks.st.attacks$triangle.transitivity)
  ks.dci.attacks<-mean(ks.st.attacks$dci)
  ks.poa.attacks<-mean(ks.attack.prop.u.d$rate.attacks)
  ks..steep.attacks<-abs(mean(ks.st.attacks$steepness))
  ks.ov.attacks<-data.frame(Knowledge.Self = c(ks.poa.attacks,ks.dci.attacks,ks.tt.attacks,ks..steep.attacks,avg.int.ks.atdu,avg.av.ks.atdu))

# Knowledge opponent
ko.st.attacks<-overall.ss.deter.uniform.attacks[overall.ss.deter.uniform.attacks$combo=="opponent rhp Uniform",]
  ko.tt.attacks<-mean(ko.st.attacks$triangle.transitivity)
  ko.dci.attacks<-mean(ko.st.attacks$dci)
  ko.poa.attacks<-mean(ko.attack.prop.u.d$rate.attacks)
  ko..steep.attacks<-abs(mean(ko.st.attacks$steepness))
  ko.ov.attacks<-data.frame(Knowledge.Opponent = c(ko.poa.attacks,ko.dci.attacks,ko.tt.attacks,ko..steep.attacks,avg.int.ko.atdu,avg.av.ko.atdu))

# History mutual
hm.st.attacks<-overall.ss.deter.uniform.attacks[overall.ss.deter.uniform.attacks$combo=="mutual history Uniform",]
  hm.tt.attacks<-mean(hm.st.attacks$triangle.transitivity)
  hm.dci.attacks<-mean(hm.st.attacks$dci)
  hm.poa.attacks<-mean(hm.attack.prop.u.d$rate.attacks)
  hm..steep.attacks<-abs(mean(hm.st.attacks$steepness))
  hm.ov.attacks<-data.frame(History.Mutual = c(hm.poa.attacks,hm.dci.attacks,hm.tt.attacks,hm..steep.attacks,avg.int.hm.atdu,avg.av.hm.atdu))

# History self
hs.st.attacks<-overall.ss.deter.uniform.attacks[overall.ss.deter.uniform.attacks$combo=="self history Uniform",]
  hs.tt.attacks<-mean(hs.st.attacks$triangle.transitivity)
  hs.dci.attacks<-mean(hs.st.attacks$dci)
  hs.poa.attacks<-mean(hs.attack.prop.u.d$rate.attacks)
  hs..steep.attacks<-abs(mean(hs.st.attacks$steepness))
  hs.ov.attacks<-data.frame(History.Self = c(hs.poa.attacks,hs.dci.attacks,hs.tt.attacks,hs..steep.attacks,avg.int.hs.atdu,avg.av.hs.atdu))

# History opponent
ho.st.attacks<-overall.ss.deter.uniform.attacks[overall.ss.deter.uniform.attacks$combo=="opponent history Uniform",]
  ho.tt.attacks<-mean(ho.st.attacks$triangle.transitivity)
  ho.dci.attacks<-mean(ho.st.attacks$dci)
  ho.poa.attacks<-mean(ho.attack.prop.u.d$rate.attacks)
  ho..steep.attacks<-abs(mean(ho.st.attacks$steepness))
  ho.ov.attacks<-data.frame(History.Opponent = c(ho.poa.attacks,ho.dci.attacks,ho.tt.attacks,ho..steep.attacks,avg.int.ho.atdu,avg.av.ho.atdu))

# Generate overall data frame of the summary tables above:
overall.u.st.attacks<-data.frame(kno.mut=km.ov.attacks,hist.mut=hm.ov.attacks,kno.self=ks.ov.attacks,hist.self=hs.ov.attacks,kno.opp=ko.ov.attacks,hist.opp=ho.ov.attacks)
row.names(overall.u.st.attacks)<-c("Rate of Attacks","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.u.st.attacks,"~/SET/YOUR/FILEPATH/overall_uniform_attacks_summary_table_dc.csv")
```



## Initiator Wins Summary Tables For Publication
```{r}
#Subset attack proportions data into individual data frames based on the distribution type and assessment information.

dist.split.i <- split(initiator.wins.prop, initiator.wins.prop$dist) #Splits attack proportions into separate data frames for "clumped" and "uniform" distributions (line 17)
new.dist.i <- c("clumped.attack.prop.i", "uniform.attack.prop.i")
for (i in 1:length(dist.split.i)) { #Variable "i" represents data by distribution
  assign(new.dist.i[i], dist.split.i[[i]]) #Assigns data to the named dataframes above (line 17)
}


clump.attack.prop.split.i <- split(clumped.attack.prop.i, clumped.attack.prop.i$combo2) #Splits attack proportions into separate data frames that occurred the "clumped" distribution based on assessment information (lines 21:26)
new.names.c.i <- c("hm.attack.prop.c.i","ho.attack.prop.c.i","hs.attack.prop.c.i")
for (j in 1:length(clump.attack.prop.split.i)) { #Variable "j" represents data in the clumped distribution by assessment information
  assign(new.names.c.i[j], clump.attack.prop.split.i[[j]]) #Assigns data to the named dataframes above (lines 21:26)
}


uni.attack.prop.split.i <- split(uniform.attack.prop.i, uniform.attack.prop.i$combo2) #Splits attack proportions into separate data frames that occurred the "uniform" distribution based on assessment information (lines 28:33)
new.names.u.i <- c("hm.attack.prop.u.i","ho.attack.prop.u.i","hs.attack.prop.u.i")
for (k in 1:length(uni.attack.prop.split.i)) { #Variable "k" represents data in the uniform distribution by assessment information
  assign(new.names.u.i[k], uni.attack.prop.split.i[[k]]) #Assigns data to the named dataframes above (lines 28:33)
}
```

```{r Deterministic Clumped Summary Table}
# Generate summary tables of the deterministic clumped data for publication:

# history mutual
hm.st.i<-overall.ss.deter.initiator[overall.ss.deter.initiator$combo=="mutual history clumped",]
  hm.tt.i<-mean(hm.st.i$triangle.transitivity)
  hm.dci.i<-mean(hm.st.i$dci)
  hm.poa.i<-mean(as.numeric(hm.attack.prop.c.i$attack.proportion))
  hm.steep.i<-abs(mean(hm.st.i$steepness))
  hm.ov.i<-data.frame(History.Mutual = c(hm.poa.i,hm.dci.i,hm.tt.i,hm.steep.i,avg.int.hm.ic,avg.av.hm.ic))

# history self
hs.st.i<-overall.ss.deter.initiator[overall.ss.deter.initiator$combo=="self history clumped",]
  hs.tt.i<-mean(hs.st.i$triangle.transitivity)
  hs.dci.i<-mean(hs.st.i$dci)
  hs.poa.i<-mean(as.numeric(hs.attack.prop.c.i$attack.proportion))
  hs.steep.i<-abs(mean(hs.st.i$steepness))
  hs.ov.i<-data.frame(History.Self = c(hs.poa.i,hs.dci.i,hs.tt.i,hs.steep.i,avg.int.hs.ic,avg.av.hs.ic))

# history opponent
ho.st.i<-overall.ss.deter.initiator[overall.ss.deter.initiator$combo=="opponent history clumped",]
  ho.tt.i<-mean(ho.st.i$triangle.transitivity)
  ho.dci.i<-mean(ho.st.i$dci)
  ho.poa.i<-mean(as.numeric(ho.attack.prop.c.i$attack.proportion))
  ho.steep.i<-abs(mean(ho.st.i$steepness))
  ho.ov.i<-data.frame(History.Opponent = c(ho.poa.i,ho.dci.i,ho.tt.i,ho.steep.i,avg.int.ho.ic,avg.av.ho.ic))

# Generate overall data frame of the summary tables above:
overall.c.st.i<-data.frame(hist.mut=hm.ov.i,hist.self=hs.ov.i,hist.opp=ho.ov.i)
row.names(overall.c.st.i)<-c("Proportion of Attack","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.c.st.i,"~/SET/YOUR/FILEPATH/overall_summary_table_ic.csv")
```

```{r Deterministic Uniform Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

# History mutual
hm.st.i.u<-overall.ss.deter.initiator[overall.ss.deter.initiator$combo=="mutual history Uniform",]
  hm.tt.i.u<-mean(hm.st.i.u$triangle.transitivity)
  hm.dci.i.u<-mean(hm.st.i.u$dci)
  hm.poa.i.u<-mean(as.numeric(hm.attack.prop.u.i$attack.proportion))
  hm.steep.i.u<-abs(mean(hm.st.i.u$steepness))
  hm.ov.i.u<-data.frame(History.Mutual = c(hm.poa.i.u,hm.dci.i.u,hm.tt.i.u,hm.steep.i.u,avg.int.hm.iu,avg.av.hm.iu))

# History self
hs.st.i.u<-overall.ss.deter.initiator[overall.ss.deter.initiator$combo=="self history Uniform",]
  hs.tt.i.u<-mean(hs.st.i.u$triangle.transitivity)
  hs.dci.i.u<-mean(hs.st.i.u$dci)
  hs.poa.i.u<-mean(as.numeric(hs.attack.prop.u.i$attack.proportion))
  hs.steep.i.u<-abs(mean(hs.st.i.u$steepness))
  hs.ov.i.u<-data.frame(History.Self = c(hs.poa.i.u,hs.dci.i.u,hs.tt.i.u,hs.steep.i.u,avg.int.hs.iu,avg.av.hs.iu))

# History opponent
ho.st.i.u<-overall.ss.deter.initiator[overall.ss.deter.initiator$combo=="opponent history Uniform",]
  ho.tt.i.u<-mean(ho.st.i.u$triangle.transitivity)
  ho.dci.i.u<-mean(ho.st.i.u$dci)
  ho.poa.i.u<-mean(as.numeric(ho.attack.prop.u.i$attack.proportion))
  ho.steep.i.u<-abs(mean(ho.st.i.u$steepness))
  ho.ov.i.u<-data.frame(History.Opponent = c(ho.poa.i.u,ho.dci.i.u,ho.tt.i.u,ho.steep.i.u,avg.int.ho.iu,avg.av.ho.iu))

# Generate overall data frame of the summary tables above:
overall.c.st.i.u<-data.frame(hist.mut=hm.ov.i.u,hist.self=hs.ov.i.u,hist.opp=ho.ov.i.u)
row.names(overall.c.st.i.u)<-c("Proportion of Attack","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.c.st.i.u,"~/SET/YOUR/FILEPATH/overall_summary_table_iu.csv")
```

```{r Deterministic Clumped Avoid Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

# History mutual
hm.st.i.c.avoid<-overall.ss.initiator.avoid[overall.ss.initiator.avoid$combo=="mutual history clumped",]
  hm.tt.i.c.avoid<-mean(hm.st.i.c.avoid$triangle.transitivity)
  hm.dci.i.c.avoid<-mean(hm.st.i.c.avoid$dci)
  hm.poa.i.c.avoid<-mean(as.numeric(hm.attack.prop.c.i$rate.avoids))
  hm..steep.i.c.avoid<-abs(mean(hm.st.i.c.avoid$steepness))
  hm.ov.i.c.avoid<-data.frame(History.Mutual = c(hm.poa.i.c.avoid,hm.dci.i.c.avoid,hm.tt.i.c.avoid,hm..steep.i.c.avoid,avg.int.hm.aci,avg.av.km.aci))

# History self
hs.st.i.c.avoid<-overall.ss.initiator.avoid[overall.ss.initiator.avoid$combo=="self history clumped",]
  hs.tt.i.c.avoid<-mean(hs.st.i.c.avoid$triangle.transitivity)
  hs.dci.i.c.avoid<-mean(hs.st.i.c.avoid$dci)
  hs.poa.i.c.avoid<-mean(as.numeric(hs.attack.prop.c.i$rate.avoids))
  hs..steep.i.c.avoid<-abs(mean(hs.st.i.c.avoid$steepness))
  hs.ov.i.c.avoid<-data.frame(History.Self = c(hs.poa.i.c.avoid,hs.dci.i.c.avoid,hs.tt.i.c.avoid,hs..steep.i.c.avoid,avg.int.hs.aci,avg.av.hs.aci))

# History opponent
ho.st.i.c.avoid<-overall.ss.initiator.avoid[overall.ss.initiator.avoid$combo=="opponent history clumped",]
  ho.tt.i.c.avoid<-mean(ho.st.i.c.avoid$triangle.transitivity)
  ho.dci.i.c.avoid<-mean(ho.st.i.c.avoid$dci)
  ho.poa.i.c.avoid<-mean(as.numeric(ho.attack.prop.c.i$rate.avoids))
  ho..steep.i.c.avoid<-abs(mean(ho.st.i.c.avoid$steepness))
  ho.ov.i.c.avoid<-data.frame(History.Opponent = c(ho.poa.i.c.avoid,ho.dci.i.c.avoid,ho.tt.i.c.avoid,ho..steep.i.c.avoid,avg.int.ho.aci,avg.av.ho.aci))

# Generate overall data frame of the summary tables above:
overall.c.st.i.c.avoid<-data.frame(hist.mut=hm.ov.i.c.avoid,hist.self=hs.ov.i.c.avoid,hist.opp=ho.ov.i.c.avoid)
row.names(overall.c.st.i.c.avoid)<-c("Rate of Avoids","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.c.st.i.c.avoid,"~/SET/YOUR/FILEPATH/overall_clump_avoid_summary_table_ic.csv")
```

```{r Deterministic Clumped Attacks Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

# History mutual
hm.st.i.c.attacks<-overall.ss.initiator.attacks[overall.ss.initiator.attacks$combo=="mutual history clumped",]
  hm.tt.i.c.attacks<-mean(hm.st.i.c.attacks$triangle.transitivity)
  hm.dci.i.c.attacks<-mean(hm.st.i.c.attacks$dci)
  hm.poa.i.c.attacks<-mean(as.numeric(hm.attack.prop.c.i$rate.attacks))
  hm..steep.i.c.attacks<-abs(mean(hm.st.i.c.attacks$steepness))
  hm.ov.i.c.attacks<-data.frame(History.Mutual = c(hm.poa.i.c.attacks,hm.dci.i.c.attacks,hm.tt.i.c.attacks,hm..steep.i.c.attacks,avg.int.hm.aci,avg.av.hm.aci))

# History self
hs.st.i.c.attacks<-overall.ss.initiator.attacks[overall.ss.initiator.attacks$combo=="self history clumped",]
  hs.tt.i.c.attacks<-mean(hs.st.i.c.attacks$triangle.transitivity)
  hs.dci.i.c.attacks<-mean(hs.st.i.c.attacks$dci)
  hs.poa.i.c.attacks<-mean(as.numeric(hs.attack.prop.c.i$rate.attacks))
  hs..steep.i.c.attacks<-abs(mean(hs.st.i.c.attacks$steepness))
  hs.ov.i.c.attacks<-data.frame(History.Self = c(hs.poa.i.c.attacks,hs.dci.i.c.attacks,hs.tt.i.c.attacks,hs..steep.i.c.attacks,avg.int.hs.aci,avg.av.hs.aci))

# History opponent
ho.st.i.c.attacks<-overall.ss.initiator.attacks[overall.ss.initiator.attacks$combo=="opponent history clumped",]
  ho.tt.i.c.attacks<-mean(ho.st.i.c.attacks$triangle.transitivity)
  ho.dci.i.c.attacks<-mean(ho.st.i.c.attacks$dci)
  ho.poa.i.c.attacks<-mean(as.numeric(ho.attack.prop.c.i$rate.attacks))
  ho..steep.i.c.attacks<-abs(mean(ho.st.i.c.attacks$steepness))
  ho.ov.i.c.attacks<-data.frame(History.Opponent = c(ho.poa.i.c.attacks,ho.dci.i.c.attacks,ho.tt.i.c.attacks,ho..steep.i.c.attacks,avg.int.ho.aci,avg.av.ho.aci))

# Generate overall data frame of the summary tables above:
overall.c.st.i.c.attacks<-data.frame(hist.mut=hm.ov.i.c.attacks,hist.self=hs.ov.i.c.attacks,hist.opp=ho.ov.i.c.attacks)
row.names(overall.c.st.i.c.attacks)<-c("Rate of Attacks","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks","Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.c.st.i.c.attacks,"~/SET/YOUR/FILEPATH/overall_clump_attacks_summary_table_ic.csv")
```

```{r Deterministic Uniform Avoid Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

# History mutual
hm.st.i.u.avoid<-overall.ss.initiator.avoid[overall.ss.initiator.avoid$combo=="mutual history Uniform",]
  hm.tt.i.u.avoid<-mean(hm.st.i.u.avoid$triangle.transitivity)
  hm.dci.i.u.avoid<-mean(hm.st.i.u.avoid$dci)
  hm.poa.i.u.avoid<-mean(as.numeric(hm.attack.prop.c.i$rate.avoids))
  hm..steep.i.u.avoid<-abs(mean(hm.st.i.u.avoid$steepness))
  hm.ov.i.u.avoid<-data.frame(History.Mutual = c(hm.poa.i.u.avoid,hm.dci.i.u.avoid,hm.tt.i.u.avoid,hm..steep.i.u.avoid,avg.int.hm.aiu,avg.av.hm.aiu))

# History self
hs.st.i.u.avoid<-overall.ss.initiator.avoid[overall.ss.initiator.avoid$combo=="self history Uniform",]
  hs.tt.i.u.avoid<-mean(hs.st.i.u.avoid$triangle.transitivity)
  hs.dci.i.u.avoid<-mean(hs.st.i.u.avoid$dci)
  hs.poa.i.u.avoid<-mean(as.numeric(hs.attack.prop.c.i$rate.avoids))
  hs..steep.i.u.avoid<-abs(mean(hs.st.i.u.avoid$steepness))
  hs.ov.i.u.avoid<-data.frame(History.Self = c(hs.poa.i.u.avoid,hs.dci.i.u.avoid,hs.tt.i.u.avoid,hs..steep.i.u.avoid,avg.int.hs.aiu,avg.av.hs.aiu))

# History opponent
ho.st.i.u.avoid<-overall.ss.initiator.avoid[overall.ss.initiator.avoid$combo=="opponent history Uniform",]
  ho.tt.i.u.avoid<-mean(ho.st.i.u.avoid$triangle.transitivity)
  ho.dci.i.u.avoid<-mean(ho.st.i.u.avoid$dci)
  ho.poa.i.u.avoid<-mean(as.numeric(ho.attack.prop.c.i$rate.avoids))
  ho..steep.i.u.avoid<-abs(mean(ho.st.i.u.avoid$steepness))
  ho.ov.i.u.avoid<-data.frame(History.Opponent = c(ho.poa.i.u.avoid,ho.dci.i.u.avoid,ho.tt.i.u.avoid,ho..steep.i.u.avoid,avg.int.ho.aiu,avg.av.ho.aiu))

# Generate overall data frame of the summary tables above:
overall.u.st.i.u.avoid<-data.frame(hist.mut=hm.ov.i.u.avoid,hist.self=hs.ov.i.u.avoid,hist.opp=ho.ov.i.u.avoid)
row.names(overall.u.st.i.u.avoid)<-c("Rate of Avoids","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.u.st.i.u.avoid,"~/SET/YOUR/FILEPATH/overall_uniform_avoid_summary_table_iu.csv")
```

```{r Deterministic Uniform Attacks Summary Table}
# Generate summary tables of the deterministic uniform data for publication:

# History mutual
hm.st.i.u.attacks<-overall.ss.initiator.attacks[overall.ss.initiator.attacks$combo=="mutual history Uniform",]
  hm.tt.i.u.attacks<-mean(hm.st.i.u.attacks$triangle.transitivity)
  hm.dci.i.u.attacks<-mean(hm.st.i.u.attacks$dci)
  hm.poa.i.u.attacks<-mean(as.numeric(hm.attack.prop.c.i$rate.attacks))
  hm..steep.i.u.attacks<-abs(mean(hm.st.i.u.attacks$steepness))
  hm.ov.i.u.attacks<-data.frame(History.Mutual = c(hm.poa.i.u.attacks,hm.dci.i.u.attacks,hm.tt.i.u.attacks,hm..steep.i.u.attacks,avg.int.hm.atiu,avg.av.hm.atiu))

# History self
hs.st.i.u.attacks<-overall.ss.initiator.attacks[overall.ss.initiator.attacks$combo=="self history Uniform",]
  hs.tt.i.u.attacks<-mean(hs.st.i.u.attacks$triangle.transitivity)
  hs.dci.i.u.attacks<-mean(hs.st.i.u.attacks$dci)
  hs.poa.i.u.attacks<-mean(as.numeric(hs.attack.prop.c.i$rate.attacks))
  hs..steep.i.u.attacks<-abs(mean(hs.st.i.u.attacks$steepness))
  hs.ov.i.u.attacks<-data.frame(History.Self = c(hs.poa.i.u.attacks,hs.dci.i.u.attacks,hs.tt.i.u.attacks,hs..steep.i.u.attacks,avg.int.hs.atiu,avg.av.hs.atiu))

# History opponent
ho.st.i.u.attacks<-overall.ss.initiator.attacks[overall.ss.initiator.attacks$combo=="opponent history Uniform",]
  ho.tt.i.u.attacks<-mean(ho.st.i.u.attacks$triangle.transitivity)
  ho.dci.i.u.attacks<-mean(ho.st.i.u.attacks$dci)
  ho.poa.i.u.attacks<-mean(as.numeric(ho.attack.prop.c.i$rate.attacks))
  ho..steep.i.u.attacks<-abs(mean(ho.st.i.u.attacks$steepness))
  ho.ov.i.u.attacks<-data.frame(History.Opponent = c(ho.poa.i.u.attacks,ho.dci.i.u.attacks,ho.tt.i.u.attacks,ho..steep.i.u.attacks,avg.int.ho.atiu,avg.av.ho.atiu))

# Generate overall data frame of the summary tables above:
overall.u.st.i.u.attacks<-data.frame(hist.mut=hm.ov.i.u.attacks,hist.self=hs.ov.i.u.attacks,hist.opp=ho.ov.i.u.attacks)
row.names(overall.u.st.i.u.attacks)<-c("Rate of Attacks","Directional Consitancy Index","Triangle Transitivity","Steepness", "Average Attacks", "Average Avoids")

# Write .csv file of the overall data frame to create summary table:
write.csv(overall.u.st.i.u.attacks,"~/SET/YOUR/FILEPATH/overall_uniform_attacks_summary_table_iu.csv")
```
