---
title: "Untitled"
author: "C.J. O'Connor-Coates"
date: "2023-06-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#X-LABELS FOR FIGURES
x.lab<-c("Mutual History","Mutual History","Mutual RHP","Mutual RHP","Opponent History","Opponent History","Opponent RHP","Opponent RHP","Self History","Self History","Self RHP","Self RHP")


#PROPORTION OF ATTACK
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(Rmisc)

setwd("~/Desktop")

sf.deter.prop_attack.fig<-attack.prop.sf.2 %>%
  ggplot( aes(x=combo2, y=as.numeric(proportion.attacking),color=resource.dist)) +
    geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=resource.dist),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Proportion of Attack") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    
    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=0.05, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(0.1,0.65))
jpeg("sf.deter.prop_attack.fig.jpeg", 336, 336)
sf.deter.prop_attack.fig
dev.off()

sf.deter.prop_attack.fig



#RATE OF AVOIDS
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(Rmisc)


setwd("~/Desktop")
rate.avoids.fig<-attack.prop.sf.2 %>%
  ggplot( aes(x=combo2, y=rate.avoids,color=resource.dist)) +
    geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=resource.dist),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Rate of Avoids") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    
    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.16, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.1,0.65))
jpeg("rate.avoids.fig.jpeg", 336, 336)
rate.avoids.fig
dev.off()

rate.avoids.fig


#RATE OF ATTACKS
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(Rmisc)


setwd("~/Desktop")
sf.rate.attacks.fig<-attack.prop.sf.2 %>%
  ggplot( aes(x=combo2, y=rate.attacks,color=resource.dist)) +
    geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=resource.dist),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Rate of Attacks") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    
    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.16, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.1,0.65))
jpeg("sf.rate.attacks.fig.jpeg", 336, 336)
sf.rate.attacks.fig
dev.off()

sf.rate.attacks.fig
    



#TRIANGLE TRANSITIVIY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

sf.deter.TTri.fig <- overall.deter.sf %>%
  ggplot( aes(x=combo2, y=triangle.transitivity,color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05, 1.05))
jpeg("sf.deter.TTri.fig.jpeg", 336, 336)
sf.deter.TTri.fig
dev.off()


#DIRECTIONAL CONSISTENCY INDEX
sf.deter.DCI.fig <- overall.deter.sf %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.deter.DCI.fig.jpeg", 336, 336)
sf.deter.DCI.fig
dev.off()
  
  
#STEEPNESS    
sf.deter.Steep.fig <- overall.deter.sf %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.deter.Steep.fig.jpeg", 336, 336)
sf.deter.Steep.fig
dev.off()

sf.deter.TTri.fig
sf.deter.DCI.fig
sf.deter.Steep.fig



#ENERGY EFFICIENCY
setwd("~/Desktop")
jpeg("sf.deter.energy_efficiency.fig.jpeg", 672, 336)
par(cex.axis=1, cex.lab=1.3, mar=c(2.65,2.75,0.4,0.4),family="sans")
sf.deter.energy_efficiency.fig<-plot(total.energy.cp.sf$energy_over_time~total.energy.cp.sf$normDS,pch=1,cex=1.4,xaxt="n",yaxt="n",col="blue",xlab="",ylab="",main="",ylim=c(0.4,0.8),xlim=c(0.85,8.25),las=1); points(total.energy.pu.sf$energy_over_time~total.energy.pu.sf$normDS,pch=2,cex=1.4,col="#CC5500"); abline(km.lm.dc.sf, lwd=3);abline(hm.lm.dc.sf, lwd=3);abline(km.lm.du.sf, col="black", lty=4, lwd=3);abline(hm.lm.du.sf, col="black", lty=4, lwd=3);title(xlab="Normalized David's Scores",line=1.25);title(ylab="Energy per unit Time", line=1.5); axis(1, at = c(0, 1, 2, 3, 4, 5, 6, 7, 8), label=rep("",9), tck=-0.015, line=0);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), label=rep("",5),tck=-0.015);axis(1, at = 1:10, line = -0.8, lwd = 0, cex.axis = 1);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), line = -0.7, lwd = 0, cex.axis = 1, las=1);box(col="black",lwd=3)
dev.off()


plot(total.energy.cp.sf$energy_over_time~total.energy.cp.sf$normDS,pch=1,cex=1.4,xaxt="n",yaxt="n",col="blue",xlab="",ylab="",main="",ylim=c(0.4,0.8),xlim=c(0.85,8.25),las=1); points(total.energy.pu.sf$energy_over_time~total.energy.pu.sf$normDS,pch=2,cex=1.4,col="#CC5500"); abline(km.lm.dc.sf, lwd=3);abline(hm.lm.dc.sf, lwd=3);abline(km.lm.du.sf, col="black", lty=4, lwd=3);abline(hm.lm.du.sf, col="black", lty=4, lwd=3);title(xlab="Normalized David's Scores",line=1.25);title(ylab="Energy per unit Time", line=1.5); axis(1, at = c(0, 1, 2, 3, 4, 5, 6, 7, 8), label=rep("",9), tck=-0.015, line=0);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), label=rep("",5),tck=-0.015);axis(1, at = 1:10, line = -0.8, lwd = 0, cex.axis = 1);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), line = -0.7, lwd = 0, cex.axis = 1, las=1);box(col="black",lwd=3)





#AVOID TRIANGLE TRANSITIVITY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}


sf.avoid.triangle.transitivity.fig <- overall.deter.sf.avoids %>%
  ggplot( aes(x=combo2, y=triangle.transitivity,color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.63, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.5, 1.05))
jpeg("sf.avoid.triangle.transitivity.fig.jpeg", 369.6, 336)
sf.avoid.triangle.transitivity.fig
dev.off()


#AVOID DCI
avoid.sf.dci.fig <- overall.deter.sf.avoids %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("avoid.sf.dci.fig.jpeg", 369.6, 336)
avoid.sf.dci.fig
dev.off()


#AVOID STEEPNESS
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}    
avoid.sf.steep.fig <- overall.deter.sf.avoids %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("avoid.sf.steep.fig.jpeg", 369.6, 336)
avoid.sf.steep.fig
dev.off()

sf.avoid.triangle.transitivity.fig
avoid.sf.dci.fig
avoid.sf.steep.fig



#ATTACK TRIANGLE TRANSITIVITY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

sf.attack.ttri.fig <- overall.deter.sf.attacks %>%
  ggplot( aes(x=combo2, y=triangle.transitivity,color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.63, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.5, 1.05))
jpeg("sf.attack.ttri.fig.jpeg", 369.6, 336)
sf.attack.ttri.fig
dev.off()


#ATTACK DCI
sf.attack.dci.fig <- overall.deter.sf.attacks %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.attack.dci.fig.jpeg", 369.6, 336)
sf.attack.dci.fig
dev.off()


#ATTACK STEEPNESS
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

sf.attack.steep.fig <- overall.deter.sf.attacks %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.attack.steep.fig.jpeg", 369.6, 336)
sf.attack.steep.fig
dev.off()

sf.attack.ttri.fig
sf.attack.dci.fig
sf.attack.steep.fig





#PROBABILITY PROPORTION OF ATTACK

library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(Rmisc)

setwd("~/Desktop")

sf.prob.prop_attack.fig<-attack.prop.sf.p.2 %>%
  ggplot( aes(x=combo2, y=as.numeric(proportion.attacking),color=resource.dist)) +
    geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=resource.dist),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Proportion of Attack") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    
    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=0.05, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(0.1,0.65))
jpeg("sf.prob.prop_attack.fig.jpeg", 336, 336)
sf.prob.prop_attack.fig
dev.off()

sf.prob.prop_attack.fig



#PROBABILITY RATE OF AVOIDS
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(Rmisc)


setwd("~/Desktop")
rate.avoids.fig<-attack.prop.sf.p.2 %>%
  ggplot( aes(x=combo2, y=rate.avoids,color=resource.dist)) +
    geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=resource.dist),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Rate of Avoids") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    
    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.16, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.1,0.65))
jpeg("rate.avoids.fig.jpeg", 336, 336)
rate.avoids.fig
dev.off()

rate.avoids.fig


#PROBABILITY RATE OF ATTACKS
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(Rmisc)


setwd("~/Desktop")
sf.rate.attacks.fig<-attack.prop.sf.p.2 %>%
  ggplot( aes(x=combo2, y=rate.attacks,color=resource.dist)) +
    geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=resource.dist),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Rate of Attacks") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    
    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.16, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.1,0.65))
jpeg("sf.rate.attacks.fig.jpeg", 336, 336)
sf.rate.attacks.fig
dev.off()

sf.rate.attacks.fig
    



#PROBABILITY TRIANGLE TRANSITIVIY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

sf.prob.TTri.fig <- overall.prob.sf %>%
  ggplot( aes(x=combo2, y=triangle.transitivity,color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05, 1.05))
jpeg("sf.prob.TTri.fig.jpeg", 336, 336)
sf.prob.TTri.fig
dev.off()


#PROBABILITY DIRECTIONAL CONSISTENCY INDEX
sf.prob.DCI.fig <- overall.prob.sf %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.prob.DCI.fig.jpeg", 336, 336)
sf.prob.DCI.fig
dev.off()
  
  
#PROBABILITY STEEPNESS    
sf.prob.Steep.fig <- overall.prob.sf %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.prob.Steep.fig.jpeg", 336, 336)
sf.prob.Steep.fig
dev.off()

sf.prob.TTri.fig
sf.prob.DCI.fig
sf.prob.Steep.fig



#PROBABILITY ENERGY EFFICIENCY
setwd("~/Desktop")
jpeg("sf.prob.energy_efficiency.fig.jpeg", 672, 336)
par(cex.axis=1, cex.lab=1.3, mar=c(2.65,2.75,0.4,0.4),family="sans")
sf.prob.energy_efficiency.fig<-plot(total.energy.cp.sf$energy_over_time~total.energy.cp.sf$normDS,pch=1,cex=1.4,xaxt="n",yaxt="n",col="blue",xlab="",ylab="",main="",ylim=c(0.4,0.8),xlim=c(0.85,8.25),las=1); points(total.energy.pu.sf$energy_over_time~total.energy.pu.sf$normDS,pch=2,cex=1.4,col="#CC5500"); abline(km.lm.dc.sf, lwd=3);abline(hm.lm.dc.sf, lwd=3);abline(km.lm.du.sf, col="black", lty=4, lwd=3);abline(hm.lm.du.sf, col="black", lty=4, lwd=3);title(xlab="Normalized David's Scores",line=1.25);title(ylab="Energy per unit Time", line=1.5); axis(1, at = c(0, 1, 2, 3, 4, 5, 6, 7, 8), label=rep("",9), tck=-0.015, line=0);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), label=rep("",5),tck=-0.015);axis(1, at = 1:10, line = -0.8, lwd = 0, cex.axis = 1);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), line = -0.7, lwd = 0, cex.axis = 1, las=1);box(col="black",lwd=3)
dev.off()


plot(total.energy.cp.sf$energy_over_time~total.energy.cp.sf$normDS,pch=1,cex=1.4,xaxt="n",yaxt="n",col="blue",xlab="",ylab="",main="",ylim=c(0.4,0.8),xlim=c(0.85,8.25),las=1); points(total.energy.pu.sf$energy_over_time~total.energy.pu.sf$normDS,pch=2,cex=1.4,col="#CC5500"); abline(km.lm.dc.sf, lwd=3);abline(hm.lm.dc.sf, lwd=3);abline(km.lm.du.sf, col="black", lty=4, lwd=3);abline(hm.lm.du.sf, col="black", lty=4, lwd=3);title(xlab="Normalized David's Scores",line=1.25);title(ylab="Energy per unit Time", line=1.5); axis(1, at = c(0, 1, 2, 3, 4, 5, 6, 7, 8), label=rep("",9), tck=-0.015, line=0);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), label=rep("",5),tck=-0.015);axis(1, at = 1:10, line = -0.8, lwd = 0, cex.axis = 1);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), line = -0.7, lwd = 0, cex.axis = 1, las=1);box(col="black",lwd=3)





#PROBABILITY AVOID TRIANGLE TRANSITIVITY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}


sf.avoid.triangle.transitivity.fig <- overall.prob.sf.avoids %>%
  ggplot( aes(x=combo2, y=triangle.transitivity,color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.63, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.5, 1.05))
jpeg("sf.avoid.triangle.transitivity.fig.jpeg", 369.6, 336)
sf.avoid.triangle.transitivity.fig
dev.off()


#PROBABILITY AVOID DCI
avoid.sf.dci.fig <- overall.prob.sf.avoids %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("avoid.sf.dci.fig.jpeg", 369.6, 336)
avoid.sf.dci.fig
dev.off()


#PROBABILITY AVOID STEEPNESS
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}    
avoid.sf.steep.fig <- overall.prob.sf.avoids %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("avoid.sf.steep.fig.jpeg", 369.6, 336)
avoid.sf.steep.fig
dev.off()

sf.avoid.triangle.transitivity.fig
avoid.sf.dci.fig
avoid.sf.steep.fig



#PROBABILITY ATTACK TRIANGLE TRANSITIVITY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

sf.attack.ttri.fig <- overall.prob.sf.attacks %>%
  ggplot( aes(x=combo2, y=triangle.transitivity,color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.63, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.5, 1.05))
jpeg("sf.attack.ttri.fig.jpeg", 369.6, 336)
sf.attack.ttri.fig
dev.off()


#PROBABILITY ATTACK DCI
sf.attack.dci.fig <- overall.prob.sf.attacks %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.attack.dci.fig.jpeg", 369.6, 336)
sf.attack.dci.fig
dev.off()


#PROBABILITY ATTACK STEEPNESS
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

sf.attack.steep.fig <- overall.prob.sf.attacks %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.attack.steep.fig.jpeg", 369.6, 336)
sf.attack.steep.fig
dev.off()

sf.attack.ttri.fig
sf.attack.dci.fig
sf.attack.steep.fig



#INITIATOR WINS TRIANGLE TRANSITIVITY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}


sf.initiator.ttri.fig <- overall.initiator.sf %>%
  ggplot( aes(x=combo2, y=abs(triangle.transitivity),color=distribution)) + 
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05, 1.05))
jpeg("sf.initiator.ttri.fig.jpeg", 336, 336)
sf.initiator.ttri.fig
dev.off()

#INITIATOR WINS DCI
sf.initiator.dci.fig <- overall.initiator.sf %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.initiator.dci.fig.jpeg", 336, 336)
sf.initiator.dci.fig
dev.off()
    
#INITIATOR WINS STEEPNESS
sf.initiator.steep.fig <- overall.initiator.sf %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.15, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.initiator.steep.fig.jpeg", 336, 336)
sf.initiator.steep.fig
dev.off()

sf.initiator.ttri.fig
sf.initiator.dci.fig
sf.initiator.steep.fig



#INITIATOR WINS AVOID TRIANGLE TRANSITIVITY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

sf.initiator.ttri.avoid.fig <- overall.initiator.sf.avoids %>%
  ggplot( aes(x=combo2, y=triangle.transitivity,color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.63, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.5, 1.05))
jpeg("sf.initiator.ttri.avoid.fig.jpeg", 369.6, 336)
sf.initiator.ttri.avoid.fig
dev.off()

#INITIATOR WINS AVOID DCI
sf.initiator.dci.avoid.fig <- overall.initiator.sf.avoids %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.initiator.dci.avoid.fig.jpeg", 369.6, 336)
sf.initiator.dci.avoid.fig
dev.off()

#INITIATOR WINS AVOID STEEPNESS
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}    
sf.initiator.steep.avoid.fig <- overall.initiator.sf.avoids %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.initiator.steep.avoid.fig.jpeg", 369.6, 336)
sf.initiator.steep.avoid.fig
dev.off()

sf.initiator.ttri.avoid.fig
sf.initiator.dci.avoid.fig
sf.initiator.steep.avoid.fig



#INITIATOR WINS ATTACKS TRIANGLE TRANSITIVITY
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

sf.initiator.ttri.attack <- overall.initiator.sf.attacks %>%
  ggplot( aes(x=combo2, y=triangle.transitivity,color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Triangle Transitivity") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.63, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.5, 1.05))
jpeg("sf.initiator.ttri.attack.jpeg", 369.6, 336)
sf.initiator.ttri.attack
dev.off()


#INITIATOR WINS ATTACKS DCI
sf.initiator.dci.attack <- overall.initiator.sf.attacks %>%
  ggplot( aes(x=combo2, y=dci,color=distribution)) +
geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Directional Consistency Index") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5, 3.5, 5.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.initiator.dci.attack.jpeg", 369.6, 336)
sf.initiator.dci.attack
dev.off()


#INITIATOR WINS ATTACKS STEEPNESS
setwd("~/Desktop")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}
sf.initiator.steep.attack <- overall.initiator.sf.attacks %>%
  ggplot( aes(x=combo2, y=abs(steepness),color=distribution)) +
  geom_boxplot(outlier.shape=NA) +
    geom_point(aes(shape=distribution),size=2.5,position=position_dodge(width=0.75))+
    scale_shape_manual(values=c(1, 2))+
    xlab("")+
    ylab("Steepness") +
    theme_bw() +
    theme(panel.grid.major.x = element_line(color = "grey",size = 0.3,linetype = 2),legend.position="none",panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.text.x=element_text(size=13, colour="black"),axis.text.y=element_text(size=12, colour="black"), panel.border=element_rect(colour="black", size=1, fill=NA), axis.title.y=element_text(size=14))+    scale_color_manual(values = c("blue","#CC5500")) +
    scale_x_discrete(limit=c("mutual rhp", "mutual history"), labels=c("RHP", "Experience"))  + 
    annotate(geom="text", x=c(1.5), y=-0.14, label=c("Mutual"), size=5)+
    coord_cartesian(expand=F, clip="off", xlim=c(0.25, 2.75), ylim=c(-0.05,1.05))
jpeg("sf.initiator.steep.attack.jpeg", 369.6, 336)
sf.initiator.steep.attack
dev.off()

sf.initiator.ttri.attack
sf.initiator.dci.attack
sf.initiator.steep.attack



#INITIATOR WINS ENERGY
setwd("~/Desktop")
jpeg("initiator.wins.energy.jpeg", 672, 336)
par(cex.axis=1, cex.lab=1.3, mar=c(2.65,2.75,0.4,0.4),family="sans")

initiator.wins.energy<-plot(total.energy.ci.sf$energy_over_time~total.energy.ci.sf$normDS,pch=1,cex=1.4,xaxt="n",yaxt="n",col="blue",xlab="",ylab="",main="",ylim=c(0.4,0.8),xlim=c(0.85,8.25),las=1); points(total.energy.iu$energy_over_time~total.energy.iu$normDS,pch=2,cex=1.4,col="#CC5500"); abline(km.lm.ci.sf, lwd=3);abline(hm.lm.ci.sf, lwd=3);abline(km.lm.ui.sf, col="black", lty=4, lwd=3);abline(hm.lm.ui.sf, col="black", lty=4, lwd=3);title(xlab="Normalized David's Scores",line=1.25);title(ylab="Energy per unit Time", line=1.5); axis(1, at = c(0, 1, 2, 3, 4, 5, 6, 7, 8), label=rep("",9), tck=-0.015, line=0);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), label=rep("",5),tck=-0.015);axis(1, at = 1:10, line = -0.8, lwd = 0, cex.axis = 1);axis(2, at = c(0.4,0.5,0.6,0.7,0.8), line = -0.7, lwd = 0, cex.axis = 1, las=1);box(col="black",lwd=3)
dev.off()


```{r}
initiator.wins.energy<-plot(total.energy.ci.sf$energy_over_time~total.energy.ci.sf$normDS,pch=1,cex=1.4,xaxt="n",yaxt="n",col="blue",xlab="",ylab="",main="",ylim=c(0.4,0.8),xlim=c(0.85,8.25),las=1); abline(km.lm.ci.sf, lwd=4);abline(hm.lm.ci.sf, lwd=3)
```
